---
title: "Predicting Home Price in Miami"
author: "David Seunglee Park and Hannah Wagner"
date: "10/10/2020"
output: 
  html_document:
    code_folding: hide
    theme: paper
    highlight: tango
    toc: true
    toc_float:
      collapsed: false
---
OUTLINE
1. introduction
  - set up
2. Data wrangling
  - make table with all datasets
  - main data
  - supplement data: coastline, bars/restaurant, crime, park, and metro data
  - census data
3. Analysis of created features
  - table with engineered features
    - one scatterplot for nn variables
    - table of slopes 
    - select nn vars for each dataset
  - map of your dependent variable (sale price)
  - 3 maps of independent variables
    - bars density map
    - map of 1 or 2 census data (NEED)
4. Test for correlation
  - correlation table with numeric values (only include selected nn vars) (NEED)
  - correlation table with census variables
  - text on highlighted relationships 
4. Model Building
  - one example model
    - provide written interpretation
  - trimmed/altered from the initial model
  - stepwise function process
  - final model (describe why we added a few more vars that we created)
    - add stargazer table with all regs models to compare
5. Cross Validation/ Results
  - test for accuracy via MAE
      - table of mean absolute error and MAPE for a single test set
  - Generalizability
      - provide result of cross validation
      - Plot of predicted prices as a function of observed prices
      - Provide a map of your residuals for your test set. 
          - Moran’s I test
          - a plot of the spatial lag in errors. 
      - Provide a map of your predicted values for where ‘toPredict’ is both 0 and 1. (NEED)
      - Using the test set predictions, provide a map of MAPE by neighborhood and possibly elementary school
      - Provide a scatterplot plot of MAPE by neighborhood as a function of mean price by neighborhood. 

6. Discussion/Conclusion

###QUESITON####
- we are not predicting expensive housings. what are the solutions for this?
- adding neighborhood makes our model worse? 

- altering zipcode information

- how to get slope of the scatter plots
- after applying neighborhood/school zone, should we test errors again?


# 1. Introduction

# 2. Set Up and Data Wrangling
```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
	echo = TRUE)

library(tidyverse)
library(sf)
library(spdep)
library(caret)
library(ckanr)
library(FNN)
library(grid)
library(gridExtra)
library(ggcorrplot)
library(jtools)
library(mapview)
library(ggstance)
library(broom.mixed)
library(osmdata)
library(geosphere)
library(tidycensus)

options(scipen=999)
options(tigris_class = "sf")
```

### 2.1 Codes for themes for map and plots

```{r, message=FALSE, warning=FALSE}

mapTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 13,colour = "black"),
    plot.subtitle=element_text(face="italic"),
    plot.caption=element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),axis.title = element_blank(),
    axis.text = element_blank(),
    axis.title.x = element_blank(),
    axis.title.y = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2)
  )
}

plotTheme <- function(base_size = 12) {
  theme(
    text = element_text( color = "black"),
    plot.title = element_text(size = 14,colour = "black"),
    plot.subtitle = element_text(face="italic"),
    plot.caption = element_text(hjust=0),
    axis.ticks = element_blank(),
    panel.background = element_blank(),
    panel.grid.major = element_line("grey80", size = 0.1),
    panel.grid.minor = element_blank(),
    panel.border = element_rect(colour = "black", fill=NA, size=2),
    strip.background = element_rect(fill = "lightskyblue1", color = "white"),
    strip.text = element_text(size=12),
    axis.title = element_text(size=12),
    axis.text = element_text(size=10),
    plot.background = element_blank(),
    legend.background = element_blank(),
    legend.title = element_text(colour = "black", face = "italic"),
    legend.text = element_text(colour = "black", face = "italic"),
    strip.text.x = element_text(size = 14)
  )
}

palette5 <- c("#25CB10", "#5AB60C", "#8FA108",   "#C48C04", "#FA7800")

qBr <- function(df, variable, rnd) {
  if (missing(rnd)) {
    as.character(quantile(round(df[[variable]],0),
                          c(.01,.2,.4,.6,.8), na.rm=T))
  } else if (rnd == FALSE | rnd == F) {
    as.character(formatC(quantile(df[[variable]]), digits = 3),
                 c(.01,.2,.4,.6,.8), na.rm=T)
  }
}

q5 <- function(variable) {as.factor(ntile(variable, 5))}
```

### 2.2 Nearest Neighbor function
```{r,message=FALSE, warning=FALSE}
nn_function <- function(measureFrom,measureTo,k) {
  measureFrom_Matrix <- as.matrix(measureFrom)
  measureTo_Matrix <- as.matrix(measureTo)
  nn <-   
    get.knnx(measureTo, measureFrom, k)$nn.dist
  output <-
    as.data.frame(nn) %>%
    rownames_to_column(var = "thisPoint") %>%
    gather(points, point_distance, V1:ncol(.)) %>%
    arrange(as.numeric(thisPoint)) %>%
    group_by(thisPoint) %>%
    summarize(pointDistance = mean(point_distance)) %>%
    arrange(as.numeric(thisPoint)) %>% 
    dplyr::select(-thisPoint) %>%
    pull()
  
  return(output)  
}
```


### 2.3 loading basemap
```{r}
# Loading Miami base map from OSM Data
miami.base <- 
  st_read("https://opendata.arcgis.com/datasets/5ece0745e24b4617a49f2e098df8117f_0.geojson") %>%
  filter(NAME == "MIAMI BEACH" | NAME == "MIAMI") %>%
  st_union()

xmin = st_bbox(miami.base)[[1]]
ymin = st_bbox(miami.base)[[2]]
xmax = st_bbox(miami.base)[[3]]  
ymax = st_bbox(miami.base)[[4]]

ggplot() +
  geom_sf(data=miami.base, fill="gray45", color = "gray20") +
  ggtitle("Miami Basemap") +
  geom_sf(data=st_as_sfc(st_bbox(miami.base)), colour="coral4", fill=NA) 
```


### 2.4 loading the main data
```{r, message=FALSE, warning=FALSE}
MiamiProperties <-
  #st_read("C:/Users/wagne/Documents/GitHub/ParkWagner_MidtermMUSA508/studentsData.geojson")%>%
  st_read("/Users/davidseungleepark/Library/Mobile Documents/com~apple~CloudDocs/Fall 2020/cpln592/ParkWagner_MidtermMUSA508/studentsData.geojson") %>%
  
  mutate(pool = ifelse(str_detect(XF1, "Pool"), "Pool", "No Pool")) %>% 
  mutate(singlefamily = ifelse(str_detect(Zoning, "SINGLE FAMILY"), "Yes", "No")) %>%
  dplyr::select(-saleDate, -saleType, -saleQual, -County.Senior, -County.LongTermSenior, -County.Other.Exempt, -Owner1, -Owner2, 
                -Mailing.Address, -Mailing.City, -Mailing.State, -Mailing.Zip, -Mailing.Country, 
                -City.Senior, -City.LongTermSenior, -City.Other.Exempt, -Legal1, -Legal2, -Legal3, -Legal4, -Legal5, -Legal6, -XF1, -XF2, -XF3,
                -WVDB, -HEX, -GPAR, -County.2nd.HEX, -City.2nd.HEX, -MillCode, -Zoning, -Land.Use)

st_crs(MiamiProperties)

# Loading elementary school boundaries 
elementary.school.boundaries <- 
  st_read("https://opendata.arcgis.com/datasets/19f5d8dcd9714e6fbd9043ac7a50c6f6_0.geojson") %>%
  st_transform('ESRI:102658')

#Neighborhood Data
neighborhood<-
  st_read("https://opendata.arcgis.com/datasets/2f54a0cbd67046f2bd100fb735176e6c_0.geojson")%>%
  st_transform('ESRI:102658')%>%
  dplyr::select(LABEL)%>%
  rename(Neighborhood=LABEL)
mapview::mapview(neighborhood)

muni_boundary<-
  st_read("https://opendata.arcgis.com/datasets/5ece0745e24b4617a49f2e098df8117f_0.geojson")%>%
  filter(NAME=="MIAMI BEACH")%>%
  st_transform('ESRI:102658')%>%
  dplyr::select(NAME)%>%
  rename(Neighborhood=NAME)
mapview::mapview(muni_boundary)

all_nhoods<-
  rbind(neighborhood,muni_boundary)
```

### 2.5 calculating coastline,bars/restaurant, crime, park, and metro data
```{r, calculating coastline,bars/restaurant, crime, park, and metro data message=FALSE, warning=FALSE}
## Calculate the distance to Coastline (this calculation has to be in WGS84)
Coastline<-opq(bbox = c(xmin, ymin, xmax, ymax)) %>% 
  add_osm_feature("natural", "coastline") %>%
  osmdata_sf()

### add to MiamiProperties and convert to miles
MiamiProperties <-
  MiamiProperties %>%
  mutate(CoastDist=(geosphere::dist2Line(p=st_coordinates(st_centroid(MiamiProperties)),
                                        line=st_coordinates(Coastline$osm_lines)[,1:2])*0.00062137)[,1])

hist(MiamiProperties$CoastDist)

##Convert Miami Data to Local Projection #st_transform('ESRI:102658')
MiamiProperties <-
  MiamiProperties%>%
  st_transform('ESRI:102658')

## Add Data on Bars, pubs, and restaurants
bars <- opq(bbox = c(xmin, ymin, xmax, ymax)) %>% 
  add_osm_feature(key = 'amenity', value = c("bar", "pub", "restaurant")) %>%
  osmdata_sf()

bars<-
  bars$osm_points%>%
  .[miami.base,]

bars<-
  bars%>%
  st_transform('ESRI:102658')
  
MiamiProperties<-
  MiamiProperties %>%
  mutate(
    bars_nn1= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(bars),1),
    bars_nn2= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(bars),2),
    bars_nn3= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(bars),3),
    bars_nn4= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(bars),4),
    bars_nn5= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(bars),5))

MiamiProperties$bars_Buffer =
  st_buffer(MiamiProperties, 660) %>%
  aggregate(mutate(dplyr::select(bars), counter = 1),., sum) %>%
  pull(counter)

MiamiProperties<-
  MiamiProperties%>%
  mutate(bars_Buffer = replace_na(bars_Buffer, 0))

## Add data on crime- Sexual Offenders and Predators within Miami-Dade County point data 
miami.sexualoffenders <-  
  st_read("https://opendata.arcgis.com/datasets/f8759d722aeb4198bfe7c4ad780604d2_0.geojson") %>%
  filter(CITY == "MIAMI" | CITY == "MIAMI BEACH" | CITY == "Miami" | CITY == "Miami Beach") %>%
  st_transform('ESRI:102658')

mapview::mapview(miami.sexualoffenders)
st_crs(miami.sexualoffenders) 

MiamiProperties$sexualoffenders_Buffer =
  st_buffer(MiamiProperties, 660) %>%
  aggregate(mutate(dplyr::select(miami.sexualoffenders), counter = 1),., sum) %>%
  pull(counter)

MiamiProperties<-
  MiamiProperties%>%
  mutate(sexualoffenders_Buffer = replace_na(sexualoffenders_Buffer, 0))

ggplot() + geom_sf(data = miami.base, fill = "grey40") +
  stat_density2d(data = data.frame(st_coordinates(miami.sexualoffenders)), 
                 aes(X, Y, fill = ..level.., alpha = ..level..),
                 size = 0.01, bins = 40, geom = 'polygon') +
  scale_fill_gradient(low = "#25CB10", high = "#FA7800", name = "Density") +
  scale_alpha(range = c(0.00, 0.35), guide = FALSE) +
  labs(title = "Density of Sexual Offenders in Miami") +
  mapTheme()

MiamiProperties <-
  MiamiProperties %>% 
  mutate(
    crime_nn1= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(miami.sexualoffenders),1),
    crime_nn2= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(miami.sexualoffenders),2),
    crime_nn3= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(miami.sexualoffenders),3),
    crime_nn4= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(miami.sexualoffenders),4),
    crime_nn5= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(miami.sexualoffenders),5))

## Add the data on Park Facilities
Parks<-st_read("https://opendata.arcgis.com/datasets/8c9528d3e1824db3b14ed53188a46291_0.geojson")%>%
st_transform('ESRI:102658')
mapview::mapview(Parks)

MiamiProperties<-
  MiamiProperties %>% 
  mutate(
    parks_nn1= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(Parks),1),
    parks_nn2= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(Parks),2),
    parks_nn3= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(Parks),3),
    parks_nn4= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(Parks),4),
    parks_nn5= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(Parks),5))

MiamiProperties$parks.Buffer =
  st_buffer(MiamiProperties, 660) %>%
  aggregate(mutate(dplyr::select(Parks), counter = 1),., sum) %>%
  pull(counter)

MiamiProperties<-
  MiamiProperties%>%
  mutate(parks.Buffer = replace_na(parks.Buffer, 0))

### nn for parks 

MiamiProperties$parks.Buffer =
  st_buffer(MiamiProperties, 660) %>%
  aggregate(mutate(dplyr::select(Parks), counter = 1),., sum) %>%
  pull(counter)

MiamiProperties <- MiamiProperties %>%
  mutate(parks.Buffer = replace_na(parks.Buffer, 0))

#TOD or non-TOD; distance to transit stop?
metrorail_stop<-st_read("https://opendata.arcgis.com/datasets/ee3e2c45427e4c85b751d8ad57dd7b16_0.geojson")%>%
  st_transform('ESRI:102658')%>%
  dplyr::select(NAME)

metromover_stop<-st_read("https://opendata.arcgis.com/datasets/aec76104165c4e879b9b0203fa436dab_0.geojson")%>%
  st_transform('ESRI:102658')%>%
  dplyr::select(NAME)

metro_stops<-
  rbind(metromover_stop,metrorail_stop)

#Distance to metro_stop (Added a column for the distance to the nearest stop and a column for homes that are within 0.5 miles of a stop)
MiamiProperties<-
  MiamiProperties %>% 
  mutate(
    metro_nn1= nn_function(st_coordinates(st_centroid(MiamiProperties)),st_coordinates(metro_stops),1),
    Halfmile_metro=ifelse(metro_nn1<2640,"Halfmile_metro","Non_Halfmile_metro"))
                                                      
```


```{r, loading census data,  message=FALSE, warning=FALSE}
## Load in census data

census_api_key("41e1c0d912341017fa6f36a5da061d3b23de335e", overwrite = TRUE)


selected_vars <- c("B02001_001E", # Estimate!!Total population by race -- ##let's double check that it's okay to use this as long as we justify it
                   "B02001_002E", # People describing themselves as "white alone"
                   "B02001_003E", # People describing themselves as "black" or "african-american" alone
                   "B15001_050E", # Females with bachelors degrees
                   "B15001_009E", # Males with bachelors degrees
                   "B19013_001E", # Median HH income
                   "B25058_001E", # Median rent
                   "B06012_002E", # Total poverty
                   "B08301_001E", # People who have means of transportation to work
                   "B08301_002E", # Total people who commute by car, truck, or van
                   "B08301_010E", # Total people who commute by public transportation"
                   "B03002_012E", # Estimate Total Hispanic or Latino by race
                   "B19326_001E", # Median income in past 12 months (inflation-adjusted)
                   "B07013_001E", # Total households
                   "B07013_002E", # Total owner-occupied households
                   "B07013_003E") # total renter-occupied households

tracts18 <- 
  get_acs(geography = "tract", 
          variables = selected_vars, 
          year=2018, 
          state=12,
          county = 086,
          geometry=T, 
          output="wide") %>%
  st_transform('ESRI:102658') %>%
  rename(TotalPop = B02001_001E, 
         Whites = B02001_002E,
         Blacks = B02001_003E,
         FemaleBachelors = B15001_050E, 
         MaleBachelors = B15001_009E,
         MedHHInc = B19013_001E, 
         MedRent = B25058_001E,
         TotalPoverty = B06012_002E,
         TotalCommute = B08301_001E,
         CarCommute = B08301_002E,
         PubCommute = B08301_010E,
         TotalHispanic = B03002_012E,
         MedInc = B19326_001E,
         TotalHH = B07013_001E,
         OwnerHH = B07013_002E,
         RenterHH = B07013_003E) %>%
  dplyr::select(-NAME, -starts_with("B0"), -starts_with("B1"), -starts_with("B2")) %>%
  mutate(pctWhite = (ifelse(TotalPop > 0, Whites / TotalPop,0))*100,
         pctBlack = (ifelse(TotalPop > 0, Blacks / TotalPop,0))*100,
         pctHis = (ifelse(TotalPop >0, TotalHispanic/TotalPop,0))*100,
         pctBlackorHis = (ifelse (TotalPop>0, (Blacks+TotalHispanic)/TotalPop,0)) *100,
         pctBachelors = (ifelse(TotalPop > 0, ((FemaleBachelors + MaleBachelors) / TotalPop),0)) *100,
         pctPoverty = (ifelse(TotalPop > 0, TotalPoverty / TotalPop, 0))*100,
         pctCarCommute = (ifelse(TotalCommute > 0, CarCommute / TotalCommute,0))*100,
         pctPubCommute = (ifelse(TotalCommute > 0, PubCommute / TotalCommute,0))*100,
         pctOwnerHH = (ifelse(TotalHH > 0, OwnerHH / TotalHH,0))*100,
         pctRenterHH = (ifelse(TotalHH > 0, RenterHH / TotalHH,0))*100,
         year = "2018") %>%
  dplyr::select(-Whites, -Blacks, -FemaleBachelors, -MaleBachelors, -TotalPoverty, -CarCommute, -PubCommute, -TotalCommute, -TotalHispanic)


#merge the data into the MiamiProperties dataframe
MiamiProperties <-st_join(MiamiProperties,tracts18)

#Add Elementary School Name to Each Property
elementary.school.clean<-
  elementary.school.boundaries%>%
  dplyr::select(NAME)%>%
  rename(elem_name=NAME)

MiamiProperties<-
  MiamiProperties%>%
  st_join(elementary.school.clean)

#Add neighborhood name to each property
MiamiProperties<-
  MiamiProperties%>%
  st_join(all_nhoods)
```

# 3. Test for correlation

# 4. Model Building
```{r}
reg1 <- lm(SalePrice ~ ., data = st_drop_geometry(MiamiProperties) %>% 
                  dplyr::select(SalePrice, LotSize, Bed, Bath, Age, 
                                ActualSqFt, parks_nn1, MedRent, MedHHInc, pctWhite, pctBlack, pctHis, pctBlackorHis, pctBachelors, pool, 
                                singlefamily, pctOwnerHH, pctRenterHH, crime_nn5, milecoast, pctNoMortgage, pctOwnerSince2010, pctCarCommute, pctPubCommute, 
                                pctPoverty, Halfmile_metro, metro_nn1, sexualoffenders_Buffer, milecoast, CoastDist, pctHH200kOrMore))
summary(reg_initial)
## trimmed/ cleaned up model from the inital model

##stepwise backward function
step( lm(SalePrice ~ ., data = st_drop_geometry(MiamiProperties) %>% 
           dplyr::select(SalePrice, LotSize, Bed, Bath, Age, 
                         ActualSqFt, parks_nn1, MedRent, MedHHInc, pctWhite, pctBlack, pctHis, pctBlackorHis, pctBachelors, pool, 
                         singlefamily, pctOwnerHH, pctRenterHH, crime_nn5, milecoast, pctNoMortgage, pctOwnerSince2010, pctCarCommute, pctPubCommute, 
                         pctPoverty, Halfmile_metro, metro_nn1, sexualoffenders_Buffer, milecoast, CoastDist,pctHH200kOrMore)), direction="backward")
##output
reg3 <- step( lm(SalePrice ~ ., data = st_drop_geometry(MiamiProperties) %>% 
                           dplyr::select(SalePrice, LotSize, Bed, Bath, Age, 
                                         ActualSqFt, parks_nn1, MedRent, MedHHInc, pctWhite, pctBlack, pctHis, pctBlackorHis, pctBachelors, pool, 
                                         singlefamily, pctOwnerHH, pctRenterHH, crime_nn5, milecoast, pctNoMortgage, pctOwnerSince2010, pctCarCommute, pctPubCommute, 
                                         pctPoverty, Halfmile_metro, metro_nn1, sexualoffenders_Buffer, milecoast, pctHH200kOrMore)), direction="backward")
summary(reg3)

#crime_nn5
reg4 <- lm(SalePrice ~ ., data = st_drop_geometry(MiamiProperties) %>% 
                    dplyr::select(SalePrice, LotSize, Bed, Bath, Age, ActualSqFt, parks_nn1, MedRent, MedHHInc, pctBlackorHis, pctBachelors, pool, 
                                  singlefamily, pctOwnerHH, pctCarCommute, pctHH200kOrMore, Halfmile_metro, crime_nn5))
summary(reg4)
#crime buffer
reg5 <- lm(SalePrice ~ ., data = st_drop_geometry(MiamiProperties) %>% 
             dplyr::select(SalePrice, LotSize, Bed, Bath, Age, ActualSqFt, parks_nn1, MedRent, MedHHInc, pctBlackorHis, pctBachelors, pool, 
                            singlefamily, pctOwnerHH, pctCarCommute, pctHH200kOrMore, Halfmile_metro, sexualoffenders_Buffer))
summary(reg5)


stargazer(reg1, reg3, reg4, reg5, type = "latex")
```

# 5. Cross Validation

# 6. Predicitons
